\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-11 paper.qmd
Change eval function

vec <- stats::setNames(rep("", 6), c("number_of_bins", "number_of_observations", "total_error", "totol_error_method_2", "totol_error_method_3", "total_mse"))  ## Define column names

>>>>

vec <- stats::setNames(rep("", 4), c("number_of_bins", "number_of_observations", "total_error", "total_mse"))  ## Define column names

### 2024-01-11 paper.tex
Change eval function

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, breakable, enhanced]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi
